Improving credibility and efficiency of decision-making \\ within democratic communities via statistical quorum

### 2018-04-19 statistical-quorum.tex
Clean.
Updated abstract.

% Some optional stuff you might like/need.
\usepackage{microtype}      % Improved Tracking and Kerning
\usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}        % Cite your images correctly!
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Improving legitimacy and efficiency of decisions in democratic communities}
%\def\plainauthor{First Author, Second Author, Third Author,
%  Fourth Author, Fifth Author, Sixth Author}
\def\emptyauthor{}
\def\plainkeywords{Decision making; voting; democracy; quorum; legitimacy; statistical quorum.}
%\def\plaingeneralterms{Documentation, Standardization}

@@

\title{Improving legitimacy and efficiency \\ of decisions in democratic communities}

@@

\begin{abstract}
The Achilles heel of many major democracies is the eternal need for sufficient engagement and attention from the community.
While there have been major efforts towards increasing these attributes within the community, we explore a fundamentally
different approach: For a fixed level of community attention, how can we optimize the allocation of this attention to
maximize productivity?
We propose a novel \emph{statistical quorum}, derived using first principles, as one metric the community can use to focus
attention, in turn making the entire decision-making process dynamic.
We developed a web application centered around this metric and tested it in a 140-person community that holds weekly
councils over the course of 16 weeks.  We found that the community was able to use the web application to simultaneously
improve the legitimacy and efficiency of their decision-making process.
\end{abstract}

@@

\subsection{Usage comparison}

>>>>

% Some optional stuff you might like/need.
\usepackage{microtype}      % Improved Tracking and Kerning
\usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
%\usepackage{ccicons}        % Cite your images correctly!
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Improving credibility and efficiency of decision-making within democratic communities via statistical quorum}
%\def\plainauthor{First Author, Second Author, Third Author,
%  Fourth Author, Fifth Author, Sixth Author}
\def\emptyauthor{}
\def\plainkeywords{Decision making; voting; democracy; quorum; credibility; statistical quorum.}
%\def\plaingeneralterms{Documentation, Standardization}

@@

\title{Improving credibility and efficiency of decision-making \\ within democratic communities via statistical quorum}

@@

\begin{abstract}
The Achilles heel of many major democracies is the eternal need for sufficient engagement and attention from the community.
While there have been major efforts towards increasing these attributes within the community, we explore a fundamentally
different approach: For a fixed level of community attention, how can we optimize the allocation of this attention to
maximize productivity?
We propose a novel \emph{statistical quorum}, derived using first principles, as one metric the community can use to
focus attention, in turn making the entire decision-making process dynamic.
We developed an online system centered around this metric and tested it in a 140-person community that holds weekly
councils over the course of 16 weeks.
We found that the community was able to use the online system to simultaneously improve the credibility and efficiency
of their decision-making process.
\end{abstract}

@@

\subsection{Use in Practice}
